\chapter{Conclusion}
After the completion of the project, it is time to conclude on the experiences and new knowledge achieved. In the beginning of the report a problem definition was created and this chapter will conclude on that content, showing how the different issues were addressed. Below the problem definition is included together with answers on how this was solved in the project.

\textbf{Problem statement:}\\
The group decided that in order to succeed, the final program should meet the following sets of requirements:

\begin{itemize}
\item Low maintenance: the program should be easy set up and use for the library staff.
\item Fits with the theme of Hj{\o}rring Library during December: Christmas. The program should be ready for the beginning of December.
\item It should be engaging for short periods of time, as well as for multiple uses. Multiple people should be able to use it simultaneously.
\item The program would be written in C++ and using the OpenCV library for reading/writing images, but all of the image processing functionality should be written by the group.
\end{itemize}

\textit{The parts from the problem definition will be illustrated by bullet points throughout this chapter and commented upon.}

\begin{itemize}
\item Low maintenance: the program should be easy set up and use for the library staff.
\end{itemize}
Low maintenance is a key factor and is of importance as setting up the installation should not take much of the staff at the library's time. This was solved by making it as simple as possible. The only thing that is required from the staff is to press three buttons to turn on the setup. This is explained in a three stepped guide:
\begin{enumerate}
\item Press button 1 - on/off button for electricity for the setup.
\item Press button 2 - on/off button on the projector.
\item Press button 3 - on/off button on the computer.
\end{enumerate}

Once these three steps are completed the computer will start up and automatically open a batch file when as Windows is done running drivers. This batch file opens the program which will initialize itself. Then after 15 seconds it will open Unity and the magic canvas is ready to use. This was a very satisfying step for the group and the staff at the library, as it meant less time on maintenance.\\ 
When turning off the installation, the same three steps are to be followed only in reverse order:
\begin{enumerate}
\item Press button 1 - on/off button on the computer.
\item Press button 2 - on/off button on the projector (Do this twice to turn it off).
\item Press button 3 - on/off button for electricity for the setup.
\end{enumerate}
Ultimately this should prevent errors and make it possible for the staff and the library to initialize the program without requiring assistance from the associated project group.


\begin{itemize}
\item Fits the theme of Hj{\o}rring Library during December: Christmas. The program should be ready for the beginning of December.
\end{itemize}
To make the installation fit the theme of Hj{\o}rring Library during December month, Christmas was brought into the project. The graphics implemented in Unity; were added to bring and generate a Christmas mood. This was done by implementing some commonly known Christmas icons/symbols - such as snow and Christmas trees. Additionally Christmas characters such as pixies and a snowman were added.\\
As a part of the final testing, visitors of the library were asked whether the installation fit the library. Gratifying for the group almost every participant answered that it did indeed fit in the library and the overall Christmas theme, which is very satisfying for the group. Besides the Christmas theme, Hj{\o}rring Library is known for being modern and appealing to their visitors. Interaction is a keyword at the library, which fits the theme of the third semester perfectly. Considering above-mentioned facts accounted for, it has been concluded that the "Magic Canvas" fits the library and the Christmas theme. 


\begin{itemize}
\item It should be engaging for short periods of time, as well as for multiple uses. Multiple people should be able to use it simultaneously.
\end{itemize}
The installation at Hj{\o}rring Library gives the user the liberty to decide themselves, how much time they would like to spend on the installation. There are no requirements needed to use the installation. All one needs is to walk in between the LED-strip positioned under the red interior of the library and the infrared camera.\\
The user is simply able to walk past the canvas seeing the character move and then decide whether she/he finds it entertaining. The fact that there are multiple character; selected randomly creates an interesting touch to the installation, as there is always one character one would rather have. This option is also possible though more than one person is using the installation. However sometimes an error occurs if 

The user will be able to just walk past the canvas seeing the character move, and then if he/she finds it entertaining then it is possible to play with, walking back and forth controlling the character. The fact that there are multiple characters which comes randomly makes it interesting to play with more than just once.\\
As for multiple persons using it simultaneously this works. The only problem is some errors if more persons walks too close to each other, since they will be recognized as one person instead of multiple persons.


\begin{itemize}
\item It should be engaging for short periods of time, as well as for multiple uses. Multiple people should be able to use it simultaneously.
\end{itemize}
The installation gives the opportunity for the user to chose how much time they want to spend on it. There is no ending so it is not required for you to spend a certain amount of time. \\
The user will be able to just walk past the canvas seeing the character move, and then if he/she finds it entertaining then it is possible to play with, walking back and forth controlling the character. The fact that there are multiple characters which comes randomly makes it interesting to play with more than just once.\\
As for multiple persons using it simultaneously this works. The only problem is some errors if more persons walks too close to each other, since they will be recognized as one person instead of multiple persons.

\begin{itemize}
\item The program would be written in C++ and using the OpenCV library for reading/writing images, but all of the image processing functionality should be written by the group.
\end{itemize}
All image processing functionality was written by the group itself, and the OpenCV library was only used to read images. However the code was not written in C++ only. All image processing was written in C++ but the visualisation is done in the program Unity using C\# code.

\textbf{Is it possible to make an interactive piece of software that fits into the environment of Hj{\o}rring Library?}\\
As this project proves - it is indeed possible. This project has shown that it is possible to make an interactive piece of software that fits into Hj{\o}rring library's environment.\\
Answers from interviews of test persons proved that Hj{\o}rring library is a great location for such a project, however it should be more highlighted to get more attention. \\
The project period has been a positive experience for the group, but also for the library. It has been a great experience to work professionally with a real library, and it encouraged the group to work even harder to get a good product. The pressure it lays on your shoulders to have to hand in a working product is a great motivation for working hard. \\
As mentioned it was a great experience for the library as well. In the mail attached below the library staff tells how this has been a valuable experience for them.

\begin{fancyquotes}
E-mail December 13, 2012\\
Tak tak, det skal vi nok klare!\\

Og tak for jeres indsats!\\
M{\aa}ske f{\o}ler I at det drukner lidt i alt jullehall{\o}jet her hos os, men for os er det en v{\ae}rdifuld erfaring. Som I kan se s{\aa} er de andre juletiltag og udstillinger lidt mere traditionelle og mere til at kigge p{\aa}. Og for os, og brugerne, er det vigtigt at vi er {\aa} alsidige som muligt, og hele tiden afpr{\o}ver nyt.\\

Med venlig hilsen
Tone Lunden
\end{fancyquotes}

