\section{Hj{\o}rring Library}
Hj{\o}rring Library aims to be a library that differs from most other Danish libraries. This is seen by the fact that it is located inside a big shopping mall, and by their passion for being interactive. Among other things the library has its own cafeteria and bar where people can show up and eat their lunch, drink coffee or have a beer after work. The architecture also appears very modern; everything is in one big room, and there are many places for people to entertain themselves with other things than just traditional books. \\ Hj{\o}rring Library wants to be a place where people can "hang out" and relax, but also have fun or work. There are many unique pieces of furniture, creating a great environment for all purposes, and especially kids can have a fun time playing games (physical and digital) and record videos in the children zone.

Hj{\o}rring Library approximately gets 1000+ visitors every day, and the goal is to give them a new and exiting experience every time they visit. One way to achieve this is by having various themes that run throughout the whole library, changing every six weeks. These includes topics such as: Arabia, birds, fairy tales and brown. The library will be decorated after these themes, so for example while the bird-theme was running all kinds of birds was exhibited around in the library, and bird songs was playing on speakers around the library.\\
These themes is an example of Hj{\o}rring Library eager to be experienced as the idea of serendipity, which basically describes a happy accident; something you didn't expect but turned out to be a pleasant surprise.

Hj{\o}rring Library is always looking for new projects that involves its visitors in new and engaging ways. Previously they have had Medialogy students come and do projects, and it turned out to be a success, so they are eager to try it out again. This is where our group comes into the picture. To us, this is a great opportunity to try making a project in a "real-life" setting where people outside of the university will engage with our product.

In the period of this project Library Hj{\o}rring has chosen the topic of Christmas. This theme runs from the second week of November until the last week of December, 2012.

\section{Interactive expo}

\section{Target group analysis}
Maybe?